Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
some changes in section 3 by yny

We begin with two identical vesicles forming a doublet under an
adhesion potential in a quiescent flow as described in
Section~\ref{sec:qflow}.  Once a doublet forms and reaches an
equilibrium configuration, we turn on the fluid trap with the stagnation
point placed at the center of the vesicle doublet.  At low extensional
rates, we expect the vesicle doublet to stay at the fluid
trap stagnation point.  On the other hand, the vesicle doublet may
become unstable and eventually separate at higher extensional rates.
Thus we expect there to exist a critical extensional rate $\chi_c$ above which
the vesicle doublet cannot stay bound under a given adhesion potential.
Therefore, the dependence of the critical extensional rate $\chi_c$ on the
adhesion potential and the mechanical vesicle properties provides a
means to probe the physics of membrane adhesion.

@@

We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
0.90, and 0.95, all with a length of $2\pi$, and we vary the extensional
rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation
point can be controlled in an experimental
setting~\cite{Johnson-Chavarria2011_EMJ}, we mimic the active control
algorithm in the microfluidic experiments by moving the center of the
doublet at each time step so that the stagnation point occurs exactly in
the middle of the doublet.  With this adjustment, the vesicles either
remain as a doublet in the fluid trap centered around the stagnation
point, or the doublet is broken and the vesicles separate from one
another.  In Figures~\ref{fig:extensional1}--\ref{fig:extensional3},
snapshots of a fluid trap containing a vesicle doublet of reduced area
$\Delta A = 0.7$ are simulated at different extensional rates.  While
this doublet remains trapped around the stagnation point for all the
considered extensional rates, a doublet with a reduced area of $\Delta A
= 0.8$ is broken with an extensional rate $\chi = 0.1$
(Figure~\ref{fig:extensional4}).  We summarize the reduced areas and
extensional rates that result in a fluid trap in left plot of
Figure~\ref{fig:extensionalPhaseDiagram}. Parameter values with a blue
mark result in a fluid trap and parameter values with a red mark result
in vesicle separation.

>>>>

We begin with two identical vesicles forming a doublet under an
adhesion potential in a quiescent flow as described in
Section~\ref{sec:qflow}.  Once a doublet forms and reaches an
equilibrium configuration, we turn on the fluid trap with the stagnation
point placed at the center of the vesicle doublet.  
When the long axis of the vesicle doublet is aligned with the far-field diverging flow, the converging flow
pushes vesicles towards each other and the repulsive interaction is essential to keep the two vesicles at the separation distance.
In this configuration the extensional flow is pushing the vesicles together. With the stagnation point placed at the center of the doublet, this
configuration appears to be quite stable for low extensional flow rate.

However, when the long axis of vesicle doublet is parallel
to the far-field converging flow, the diverging flow may overcome the vesicle adhesion to
split the two vesicles apart. Thus in the following simulation experiments we place the vesicle doublet so that the flat contact region is
aligned with the axis of converging flow. In this configuration the flow is pulling the vesicles away from each and 
is expected to be less stable than the orthogonal configuration where the fluid flow is constantly pushing vesicles towards each other. 
It is also reasonable to expect the vesicle doublet to rotate around the stagnation so the flow is pushing them together rather than pulling them apart.

At low extensional
rates, we expect the vesicle doublet to stay at the fluid
trap stagnation point.  On the other hand, the vesicle doublet may
become unstable and eventually separate at higher extensional rates.
Thus we expect there to exist a critical extensional rate $\chi_c$ above which
the vesicle doublet cannot stay bound under a given adhesion potential.
Therefore, the dependence of the critical extensional rate $\chi_c$ on the
adhesion potential and the mechanical vesicle properties provides a
means to probe the physics of membrane adhesion.

@@

We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
0.90, and 0.95, all with a length of $2\pi$, and we vary the extensional
rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation
point can be controlled in an experimental
setting~\cite{Johnson-Chavarria2011_EMJ}, we mimic the active control
algorithm in the microfluidic experiments by moving the center of the
doublet at each time step so that the stagnation point occurs exactly in
the middle of the doublet.  
With this adjustment, the vesicles either
remain as a doublet in the fluid trap centered around the stagnation
point, or the doublet is broken and the vesicles separate from one
another.

In Figures~\ref{fig:extensional1}--\ref{fig:extensional3},
snapshots of a fluid trap containing a vesicle doublet of reduced area
$\Delta A = 0.7$ are simulated at different extensional rates.  While
this doublet remains trapped around the stagnation point for all the
considered extensional rates, a doublet with a reduced area of $\Delta A
= 0.8$ is broken with an extensional rate $\chi = 0.1$
(Figure~\ref{fig:extensional4}).  We summarize the reduced areas and
extensional rates that result in a fluid trap in left plot of
Figure~\ref{fig:extensionalPhaseDiagram}. Parameter values with a blue
mark result in a fluid trap and parameter values with a red mark result
in vesicle separation.
